Home

### 2023-06-11 analysis/Paper_Suppl_figures_simulation.Rmd
fix link bug

>>>>

## Additional plots for revision, just PIP plots
```{r PIPplot2, fig.width= 8, fig.height= 18}
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20220322/"
# simu 1-x and 2-x, SNP PVE = 0.1
# simu 7,11,8,9, SNP PVE =0.2
simutaglist = c(lapply(1:2, function(x) paste(x, 1:5, sep ="-")),
                list(paste(c(7,11,8,9), 1:20, sep = "-")))
pdf(file = "temp3.pdf", height = 25, width =3)
plotlist <- list()
for (i in 1:length(simutaglist)){
  plotlist[[i]] <- plot_PIP(configtag, runtag, simutaglist[[i]], main = "")
}

outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20220321/"
simutaglist = c(lapply(1:2, function(x) paste(x, 1:5, sep ="-")),
                list(paste(c(7,11,8,9), 1:20, sep = "-")))
pdf(file = "temp3.pdf", height = 25, width =3)
plotlist <- list()
for (i in 1:length(simutaglist)){
  plotlist[[i]] <- plot_PIP(configtag, runtag, simutaglist[[i]], main = "")
}

gridExtra::grid.arrange(plotlist[[1]], plotlist[[2]],
                        plotlist[[3]], plotlist[[4]],
                        plotlist[[5]], plotlist[[6]],
                        plotlist[[7]], plotlist[[8]],
                        plotlist[[9]], plotlist[[10]],
                        ncol = 2)
dev.off()
```

### 2023-06-11 analysis/index.Rmd
fix link bug

* [**Using UKbiobank data (110k samples), fusion weights Adipose, more settings with low SNP PVE **](simulation-ctwas-ukbWG-gtex.adipose_s200.113_03221023.html)

>>>>

* [**Using UKbiobank data (110k samples), fusion weights Adipose, more settings with low SNP PVE **](simulation-ctwas-ukbWG-gtex.adipose_s200.113_03212023.html)
